On the formation of H$\alpha$ line emission around classical T Tauri stars

### 2006-01-26 TTau_Halpha/kurosawa.tex
Minor update.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@634 25464f21-6099-402c-b30a-640f1d40d38b

Because of the geometrical constraints imposed by the magnetosphere
and the disc wind, the finite height of the $\alpha$ disc causes an
undesirable interface problem at the boundary; hence, the inner part
($R_{\mathrm{di}} < w < R_{\mathrm{wo}}$) of the disc is replaced by
the geometrically thin (but opaque) disc. Since the emissivity of the
disc at the optical wavelength is negligible and the disc scale height
is relatively small in the inner part of disc, this replacement is
reasonable.  On the other hand, the finite height of the disc at the
outer part is important for determining the shape of the H$\alpha$
profiles observed at high inclinations, as we will see in section~XXX.

>>>>

Because of the geometrical constraints imposed by the magnetosphere
and the disc wind, the finite height of the $\alpha$ disc causes an
undesirable interface problem at the boundary; hence, the inner part
($R_{\mathrm{di}} < w < R_{\mathrm{wo}}$) of the disc is replaced by
the geometrically thin (but opaque) disc. Since the emissivity of the
disc at the optical wavelength is negligible and the disc scale height
is relatively small in the inner part of disc, this replacement is
reasonable.  On the other hand, the finite height of the disc at the
outer part is important for determining the shape of the H$\alpha$
profiles observed at high inclinations.
